Active Code Completion

### 2012-03-19 icse12/graphite-icse12.tex
Added some related work to icse12

\usepackage{alltt}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0 0}}

@@

Several refinements and additions to the code completion menu have previously been suggested in the literature. These have focused on leveraging additional sources of information, such as databases of usage history \cite{robbes_how_2008}, examples extracted from code repositories \cite{bruch_learning_2009} and crowdsourced information \cite{mooty_calcite:_2010}, to increase the relevance and sophistication of the featured menu items. As with the standard form of code completion, many of these sources of data can also be utilized via external tools (e.g. Calcite \cite{mooty_calcite:_2010} uses information that could already be accessed using the Jadeite \cite{conf/vl/StylosFYM09} tool). Empirical evidence presented in these studies, however, indicates that directly integrating these kinds of tools directly into the editor environment can be more effective.

>>>>

\usepackage{alltt}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}}

@@

Several refinements and additions to the code completion menu have previously been suggested in the literature. These have focused on leveraging additional sources of information, such as databases of usage history \cite{robbes_how_2008}\cite{HouPletcher2011}, inheritance information \cite{HouPletcher2011}, API-specific information \cite{HouPletcher2011}\cite{Lee+2008}, partial abbreviations \cite{Han+2009}, examples extracted from code repositories \cite{bruch_learning_2009} and crowdsourced information \cite{mooty_calcite:_2010}, to increase the relevance and sophistication of the featured menu items. As with the standard form of code completion, many of these sources of data can also be utilized via external tools (e.g. Calcite \cite{mooty_calcite:_2010} uses information that could already be accessed using the Jadeite \cite{conf/vl/StylosFYM09} tool). Empirical evidence presented in these studies, however, indicates that directly integrating these kinds of tools directly into the editor environment can be more effective.
